% 英文摘要
The abstract is the epitome of the thesis, and it is a high-level summary and condensation of the full text, which is convenient for readers to understand the outline of the full text. Abstracts are also a medium for expanding circulation. Some intelligence personnel compile index materials based on the abstracts of papers, and some compile them into abstract publications, so that the scope of circulation will be greatly expanded.

The abstract of the thesis contains five aspects: the background of the thesis topic (the purpose of the research); the content of the research to solve the problem); the research methods used; the results of the research; the main conclusions of the research and their significance.

The abstract is a short essay for completeness and self-containedness, without comments and supplementary explanations. The length of the abstract should not be less than half a page and within 3000 words. Special attention: Do not write the background, the importance of the problem, etc. in the abstract (this part should not exceed a quarter of the length of the abstract).

The language of the abstract must be outlined, concise, and focused. Chinese abstracts do not use the first-person tone, such as "this article", "we", "we", etc., but need to use the third-person tone. In the English abstract, it is mentioned that this paper can use this thesis or this dissertation, but do not use this paper.

Note that expressions such as "This article has X chapters, Chapter 1..., Chapter 2..." should not appear in the abstract.

Do not cite references in the abstract.

By Google Translate.
